\section{Efficiency, 市场效率}
\textbf{Efficiency} is reached when costs are minimized, both to individuals (productive efficiency) and the society (allocative efficiency).

\subsection{Productive Efficiency}
This refers to minimizing input holding output constant (LRAC) or maximizing output holding input constant (PPC). \\
Two types of productive efficiency include:
\begin{quote}
    1. Firm productive efficiency: each firm on LRAC; \\
    2. Industry productive efficiency: each firm has the same MC (no reallocation of output can lower costs)
\end{quote}
If all firms and industries are producing efficiently, the economy is productively efficient, thus, on PPC (Economy Allocative Efficiency: at the optimal point of PPC).

\subsection{Allocative Efficiency}
This means Pareto efficiency/optimality, exchange efficiency, and market efficiency. \\
This is: minimizing the cost to society, referring to the mix of commodities produced, where consumer and producer coincide in preferences. \\
For allocative efficiency, we need
$$P = MB = MC$$
thus, firms must be perfectly competitive, there is no DWSL. \\
Any point on the PPC represents productive efficiency, but only one point on the PPC reaches allocative efficiency.

\subsection{Efficiency in Perfect Competition and Monopoly}
Perfect competition market structure can reach both productive efficiency and allocative efficiency. \\
Monopoly market structure can reach productive efficiency (on LRAC, just not minimum), but cannot reach allocative efficiency ($P > MC$, there is a DWSL). However, a perfectly price-discriminating monopoly can reach both. \\
Single-price monopolies may "offset" the increase in price by reducing costs, therefore, reducing certain DWSL. \\
It is important to note:
\begin{quote}
    1. Efficiency is not the only goal (equity) \\
    2. Private costs can omit social costs (lead to market failure) \\
    3. Costs are not independent of market structure (Monopolies needed for economies of scale) \\
    4. Monopolies may be needed for innovation.
\end{quote}

\newpage